---
title: "p8105_hw6_wq2160"
author: "Wenshan Qu (wq2160)"
date: "11/26/2021"
output: github_document
---

```{r include = FALSE}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

**Read and Tidy Data**

```{r message = FALSE}
birthweight_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    babysex = factor(babysex, levels = c("1", "2")),
    frace = factor(frace, levels = c("1", "2", "3", "4", "8", "9")),
    malform = factor(malform, levels = c("0", "1")),
    mrace = factor(mrace, levels = c("1", "2", "3", "4", "8")),
    parity = as.integer(parity)
  )

birthweight_df
```

**Cheking `NA`**

```{r}
map_df(birthweight_df, ~sum(is.na(.))) %>% 
  knitr::kable(align = "c")
```

We can see that there is no `NA` value in this data.

**Fit Linear Model**

My interested predictors includes: 

  1) mother’s pre-pregnancy BMI (`ppbmi`);
  
  2) average number of cigarettes smoked per day during pregnancy (`smoken`);
  
  3) mother’s age at delivery (years) (`momage`);
  
  4) gestational age in weeks (`gaweeks`).
  
Then we fit the linear model based on above parameters.

```{r}
bw_fit = lm(bwt ~ ppbmi + smoken + momage + gaweeks, data = birthweight_df)

bw_fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable()
```

Describe modeling process: I use linear regression model to build a relationship between a dependent variable (`bwt`) and a set of independent variables (`ppbmi`, `smoken`, `momage`, `gaweeks`).

**Model Residuals against Fitted Values**

```{r}
resid_pred_df = 
  birthweight_df %>% 
  add_residuals(bw_fit) %>% 
  add_predictions(bw_fit) %>% 
  select(pred, resid)

resid_pred_df %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .5) +
  labs(
    title = "Model Residuals against Fitted Values",
    x = "Fitted Value",
    y = "Residual"
  )
```

We can see that these residuals are almost symmetric around 0, and most of them are around 0, while some of them (outliers) are around -1000 and 1000.

**Compare Models**

The first compared model: _length at birth and gestational age as predictors (main effects only)_

```{r}
fit1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)

fit1 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

The second compared model: _head circumference, length, sex, and all interactions (including the three-way interaction) between these_

```{r}
fit2 = lm(bwt ~ bhead * blength * babysex, data = birthweight_df)

fit2 %>% 
  broom::tidy() %>% 
  knitr::kable()
```

**Make this comparison in terms of the cross-validated prediction error**

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
      train = map(train, as_tibble),
      test = map(test, as_tibble)
  ) %>% 
  mutate(
      a_mod = map(.x = train, ~lm(bwt ~ ppbmi + smoken + momage + gaweeks, data = .x)),
      b_mod = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
      c_mod = map(.x = train, ~lm(bwt ~ bhead * blength * babysex, data = .x))
  ) %>% 
  mutate(
      rmse_a = map2_dbl(.x = a_mod, .y = test, ~rmse(model = .x, data = .y)),
      rmse_b = map2_dbl(.x = b_mod, .y = test, ~rmse(model = .x, data = .y)),
      rmse_c = map2_dbl(.x = c_mod, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  pivot_longer(
    rmse_a:rmse_c,
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin() +
  labs(
    title = "Comparasion between Three Different Models",
    subtitle = "a = my model, b = fit1 model, c = fit2 model",
    x = "Model", 
    y = "RMSE"
  )
```

Comment: We can see that the Model C (which is the second given model defined as `bwt ~ bhead * blength * babysex`) has the lowest RMSE and has the best fit, while Model A (which is my model, defined as `bwt ~ ppbmi + smoken + momage + gaweeks`) has the worst fit. It is quite reasonable for the Model C contains not only the main effects, but also the interactions.

## Problem 2

**Load the Data**

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

**5000 Bootstrap**

```{r warning = FALSE, message = FALSE}
boot_df = 
  weather_df %>% 
  bootstrap(n = 5000, id = "strap_number") %>% 
  mutate(
    model = map(.x = strap, ~lm(tmax ~ tmin, data = .x)),
    results_tidy = map(model, broom::tidy),
    results_glance = map(model, broom::glance)
  ) %>% 
  select(strap_number, results_tidy, results_glance) %>% 
  unnest(results_tidy, results_glance) %>% 
  janitor::clean_names() %>% 
  select(strap_number, term, estimate, r_squared) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate
  ) %>% 
  rename("beta_0" = "(Intercept)", "beta_1" = "tmin") %>% 
  mutate(
    log_beta = log(beta_0 * beta_1)
  ) %>% 
  select(strap_number, r_squared, log_beta)

boot_df
```

**Plot Estimated R Squared** 

```{r}
boot_df %>% 
  ggplot(aes(x = r_squared)) +
  geom_density() + 
  labs(
    title = "R.Squared Distribution Plot",
    x = "Estimated R.Squared",
    y = "Density"
  )
```

**Plot log(beta_0 * beta_1)**

```{r}
boot_df %>% 
  ggplot(aes(x = log_beta)) +
  geom_density() + 
  labs(
    title = "Log(beta_0 * beta_1) Distribution Plot",
    x = "log(beta_0 * beta_1)",
    y = "Density"
  )
```

